Removal only

### 2020-05-26 analysis/figure-4.Rmd
working but not ready

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(ggsignif)

@@

candidateDEGS <- allDEG %>%
  filter(gene %in% candidategenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", 
                         "gonad" = "G", "gonads" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, inc.d3_m.inc.d3, inc.d9_m.inc.d9, inc.d17_m.inc.d17, hatch_m.n2,
          inc.d17_prolong, hatch_prolong)
candidateDEGS

@@

b1 <- plotcandidatemanipquad(candidatevsd, "hypothalamus", c("DRD1")) 
b2 <- plotcandidatemanipquad(candidatevsd,"pituitary", c("PRL")) 
b3 <- plotcandidatemanipquad(candidatevsd,"gonad", c("PGR"))

b <- plot_grid(b1,b2,b3, ncol = 1)

c1 <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs(subtitle = "Hypothalamus ", x = NULL)  
c2 <- plottsneelipsev2(hyptsne, hyptsne$extint, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c3 <- plottsneelipsev2(hyptsne, hyptsne$earlylate, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank()) 
c4 <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(subtitle = "Pituitary ", x = NULL) 
c5 <- plottsneelipsev2(pittsne, pittsne$extint, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank()) 
c6 <- plottsneelipsev2(pittsne, pittsne$earlylate, allcolors ) + 
  labs(subtitle = " ", x = NULL) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c7 <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
  labs(subtitle = "Ggonads ")  
c8 <- plottsneelipsev2(gontsne, gontsne$extint, allcolors ) + 
  labs(subtitle = " " )    +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())
c9 <- plottsneelipsev2(gontsne, gontsne$earlylate, allcolors ) + 
  labs(subtitle = " " ) + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank())

c <- plot_grid(c1,c2,c3,c4,c5,c6,c7,c8,c9, nrow = 3)

bc <- plot_grid(b, c, nrow = 1, labels = c("", "C"), label_size = 8)

fig4 <- plot_grid(a, bc, ncol = 1, rel_heights  = c(0.25,1),
          labels = "AUTO", label_size = 8)
fig4

pdf(file="../figures/fig4-1.pdf", width=7.25, height=7.25)
plot(fig4)
dev.off()

candidatevsd <- candidatevsd %>%
  dplyr::mutate(treatment = fct_collapse(treatment,
                                         "m.n2" = c("m.n2",  "m.hatch" ),
                                         "prolong" = c("prolong", "inc.prolong") ,
                                         "extend" = c("extend", "extend.hatch")
                                         ))  %>%
  dplyr::mutate(day = fct_collapse(treatment,
                                    "0" = c("control", "bldg"),
                                    "1" = c("lay"),
                                     "3" = c("inc.d3", "m.inc.d3" ),
                                     "9" = c("inc.d9", "m.inc.d9", "early"  ),
                                     "17" = c("inc.d17", "m.inc.d17", "prolong"  ),
                                     "18" = c("hatch", "m.n2" ),
                                     "22" = c("n5",  "extend" ),
                                     "26" = c("n9"  )
                                     )) %>%
   mutate(treatment = factor(treatment, levels = alllevels)) %>%
  dplyr::mutate(day = factor(day, levels = c("0", "1", "3", "9", "17", "18", "22", "26")))

candidatevsd %>%
    filter(tissue == "hypothalamus", sex == "female") %>%
    filter(gene %in% "DRD1") %>%
    drop_na()  %>%
    ggplot(aes(y =  counts, x = day, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "bottom",
          #axis.text.x = element_blank(),
          #axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(subtitle = paste("female", "hypothalamus", sep = " "), y = "DRD1")

candidatevsd %>%
    filter(tissue == "pituitary", sex == "female") %>%
    filter(gene %in% "PRL") %>%
    drop_na()  %>%
    ggplot(aes(y =  counts, x = day, fill = treatment, color = sex)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(size = 0.25, aes(color = sex)) +
    theme_B3() +
    theme(legend.position = "bottom",
          #axis.text.x = element_blank(),
          #axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    scale_color_manual(values = allcolors) +
    scale_fill_manual(values = allcolors)  +
    labs(subtitle = paste("female", "pituitary", sep = " "), y = "PRL")

@@

t7 <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors) +  labs(subtitle = "Gonads ") +
  facet_wrap(~sex) + theme(strip.text = element_blank())
t8 <- plottsneelipsev2(gontsne, gontsne$extint, colorhypothesis) +  labs(subtitle = "  ")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank(), strip.text = element_blank())
t9 <- plottsneelipsev2(gontsne, gontsne$earlylate, colorhypothesis) +  labs(subtitle = "  ")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank(), strip.text = element_blank())
t789 <- plot_grid(t7, t8, t9, nrow = 1)

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(cowplot)
library(Rtsne)
library(ggsignif)
library(corrr)

@@

candidateDEGS <- allDEG %>%
  filter(gene %in% parentalcaregenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", 
                         "gonad" = "G", "gonads" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, inc.d3_m.inc.d3, inc.d9_m.inc.d9, inc.d17_m.inc.d17, hatch_m.n2,
          inc.d17_prolong, hatch_prolong)
candidateDEGS

@@

boxplots <- plot_grid(boxplots1, boxplots2, nrow = 1, rel_widths = c(1.5,1))
plot_grid(boxplots, t456, a, ncol = 1, rel_heights = c(3,1,1))

#pdf(file="../figures/fig4-1.pdf", width=7.25, height=7.25)
#plot(fig4)
#dev.off()

makecorrdf <- function(whichsex, whichtissue, whichgenes){
  corrrdf <- candidatevsd %>% 
    filter(sex == whichsex, tissue == whichtissue,
           gene %in% whichgenes) %>%
    drop_na() %>%
    pivot_wider(names_from = gene, values_from = counts) %>%
    select(-sex, -tissue, -treatment, -samples, -earlylate, -extint) %>%
    correlate() 
  print(head(corrrdf))
  return(corrrdf)
}

candidatevsd <- candidatevsd %>% filter(treatment %in% maniplevels)

hyp1 <- makecorrdf(sexlevels, "hypothalamus", curleychampagnegenes)  
pit1 <- makecorrdf(sexlevels, "pituitary", curleychampagnegenes)  
gon1 <- makecorrdf(sexlevels, "gonad", curleychampagnegenes)

hyp2 <- makecorrdf(sexlevels, "hypothalamus", GOgenes)  
pit2 <- makecorrdf(sexlevels, "pituitary", GOgenes)  
gon2 <- makecorrdf(sexlevels, "gonad", GOgenes)

hyp3 <- makecorrdf(sexlevels, "hypothalamus", cancergenes)  
pit3 <- makecorrdf(sexlevels, "pituitary", GOgecancergenesnes)  
gon3 <- makecorrdf(sexlevels, "gonad", cancergenes)

b1 <- plotcorrplot(hyp1, "Literature") + labs(title = "hyp")
b2 <- plotcorrplot(pit1, NULL)  + labs(title = "pit")
b3 <- plotcorrplot(gon1, NULL)  + labs(title = "gon")

b4 <- plotcorrplot(hyp2, "GO")  + labs(title = " ")
b5 <- plotcorrplot(pit2, NULL)   + labs(title = " ")
b6 <- plotcorrplot(gon2, NULL)  + labs(title = " ")

b7 <- plotcorrplot(hyp3, "Caner") + labs(title = " ")
b8 <- plotcorrplot(pit3, NULL)   + labs(title = " ")
b9 <- plotcorrplot(gon3, NULL)  + labs(title = " ")

forlegend <- plotcorrplot(gon3, NULL) + theme(legend.position = "bottom") + labs(color = "Correlation")
mylegend <- get_legend(forlegend)

allcorplots <- plot_grid(b1,b4,b7,
          b2,b5,b8,
          b3,b6,b9)

supplfigX <- plot_grid(allcorplots, mylegend, ncol = 1, rel_heights = c(1,0.1))
supplfigX
```

@@

t7 <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors) +  labs(subtitle = "Gonads ") +
  facet_wrap(~sex) + theme(strip.text = element_blank())
t8 <- plottsneelipsev2(gontsne, gontsne$extint, colorhypothesis) +  labs(subtitle = "  ")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank(), strip.text = element_blank())
t9 <- plottsneelipsev2(gontsne, gontsne$earlylate, colorhypothesis) +  labs(subtitle = "  ")   +
  facet_wrap(~sex) + theme(axis.title.y = element_blank(), strip.text = element_blank())
t789 <- plot_grid(t7, t8, t9, nrow = 1)
```

## write files

```{r write}
#write.csv(candidateDEGS, "../results/table2.csv", row.names = F)
```
